\begin{document}

\title{Chapter 5: The Terrible Battle of Phrobald and the Minotaur}

\begin{code}{chapter5.blok}
battle {
\end{code}

As he crested the incline, Phrobald wiped his brow and began to
regret his decision to undertake this cursed errand.  His eyes
narrowed as he surveyed the green vale from his newly taken
vantage.  The gentle roll of verdant hills, shadowless in
the noonday sun, stretched as far as the eye could see.

\begin{code}{chapter5.blok}
  hero {
    name: "Phrobald the Halfling"
    hp: Fixed { amount = 50 }
    damage: Dice { sides = 6, number = 2 }
  }
\end{code}

A dandelion seed, caressed by a whimsical air current,
drifted by Phrobald's nose.  His thoughts turned to home and
the equations that goverened it.

\begin{eqnarray}
  \rho\frac{D\mathbf{u}}{Dt} & = & - \nabla p + \nabla \cdot \boldsymbol \tau + \rho\,\mathbf{g} \\
  \frac {\partial}{\partial t} (\rho\,\mathbf{u})
   + \nabla \cdot (\rho\,\mathbf{u} \otimes \mathbf{u})
 & = & - \nabla p + \nabla \cdot \boldsymbol \tau + \rho\,\mathbf{g}
\end{eqnarray}

While lost in his reverie, Phrobald almost did not notice
the hostile footsteps behind him.  With a sigh he wheeled about to
face his foes: three ragged-looking orcs.
\textit{The fools grow bolder by the day,} thought Phrobald
before noticing the huge minotaur flanking him.

\begin{code}{chapter5.blok}
  orc {
    hp: Dice { number = 1, sides = 6 }
    damage: Fixed { amount = 2 }
  }

  orc {
    hp: Dice { number = 1, sides = 6 }
    damage: Fixed { amount = 2 }
  }

  orc {
    hp: Dice { number = 1, sides = 6 }
    damage: Fixed { amount = 2 }
  }

  minotaur {
    hp: Dice { number = 4, sides = 8 }
    damage: Dice { number = 1, sides = 8}
  }
\end{code}

Fear gripped Phrobald, but not enough that he failed to ready
his bec-de-corbin.

\begin{code}{chapter5.blok}
}
\end{code}

\end{document}